\cvsection{Experience}
\begin{cventries}
  \cventry
    {Researcher Team Member}
    {Fordham Robotics Lab}
    {Bronx, New York}
    {Mar. 2014 - May. 2016}
    {
      \begin{cvitems}
        \item {Strengthened a Space Based Potential Field Robotics algorithm by collaborating with three person team}
        \item {Established Server and Client protocols for mobile robots to communicate}
        \item {Presented at San Francisco SPIE Research Symposium as a Representative of the FRCV lab}
        \item{Spearheaded Fordham Kinect2 RGB-D based navigation project}
      \end{cvitems}
    }
  \cventry
    {Software Engineering Intern}
    {Adept Technology}
    {Amherst, New Hampshire}
    {Jun. 2015 - Aug. 2015}
    {
      \begin{cvitems}
        \item {Developed new with Kinect2 RGB-D navigation functionality to Adept’s Mobile Manipulator robot}
        \item {Mentored by Reed Hedges, Mobile Robots Software developer}
        \item {Attained a Advanced level in ROS skills}
        \item {Networked with Robotics Professionals at Adept}
      \end{cvitems}
    }
  \cventry
    {Resident Technology Consultant}
    {Fordham IT Department}
    {New York, New York}
    {Aug. 2013 - May 2014}
    {
      \begin{cvitems}
        \item {Managed IT for individual students}
        \item {Handled student + faculty technical issues:  Repaired Wifi connections, Conducted Antivirus Scans, IP refreshes}
        \item{Led IT team during move-in}
      \end{cvitems} 
    }
  \cventry
    {}
    {Freelance Web Designer}
    {New York, New York}
    {Jul. 2012 - present}
    {
      \begin{cvitems}
        \item {Designed + Populated Hamptons Real Estate Website, PropertyBones.com}
        \item{Developed AveryBart.com a professional photography website}
        \item{Improving Amoshouse.org, a local charity website: Adding Donation option, Redesigned user interface, Created Database of users and VIPs}
      \end{cvitems}
    }
  \cventry
    {Writer}
    {Zumic Entertainment Inc.}
    {Brooklyn, New York}
    {Sept. 2012 - Feb. 2013}
    {
      \begin{cvitems}
      \item{Conceptualized overall website design and projected design improvements}
      \item{Strengthened the website SEO and online marketing efforts}
      \item{Managed social media presence via Facebook, Twitter and Reddit}
      \item{Published music news articles to website}
      \item{Edited website photography}
      \end{cvitems}
    }
\end{cventries}
